---
title: "full_analysis_study2"
author: "Rose M. Schneider"
date: "4/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source(here::here("Analyses/0-clean.R")) 

# Load cleaned data - 2 dfs
## TODO clean up the csv
rm(list = ls())
study2_data <- read.csv(here::here("Data/Cleaned data/Study2_MC_iran.csv"))%>% 
  mutate(item = ifelse(item == "toys ", "toys", as.character(item)), 
         item = ifelse(task_num == "conv4.8", "toys", as.character(item)), 
         item = ifelse(task_num == "reigious1.8", "push", as.character(item)), 
         task = ifelse(item == "push", "moral", as.character(task)), 
         q_kind_label = ifelse(q_kind_label == "Farawary country", "Faraway country", 
                               ifelse(q_kind_label == "Non-muslim", "Non-Muslim", as.character(q_kind_label))))#study 2

## Libraries
library(tidyverse)
library(magrittr)
library(car)
library(lme4)
library(ggpubr)
library(broom)
library(broom.mixed)
library(lmerTest)

## Leftover data manipulations
# leftover data manipulations
study2_data %<>%
  mutate(subid = factor(subid), 
         task = factor(task), 
         item = factor(item), 
         answer = as.numeric(answer), 
         site = factor(site), 
         age.c = as.vector(scale(age, center = TRUE, scale = TRUE)), 
         age.group = as.numeric(as.character(age.group)))%>%
  mutate(age.bin = ifelse(age.group < 7, "5-6", 
                          ifelse((age.group >= 7 & age.group < 9), "7-8", "9-10")))

#global theme set
theme_set(theme_bw() + theme(text = element_text(size=13), 
                             axis.title=element_text(size=12),
                             strip.text = element_text(margin=margin(2,0,2,0)), 
                             panel.grid = element_blank()))
```

# Study 2

## Participants
### Overall age demographics
```{r}
study2_data %>%
  distinct(subid, age)%>%
  summarise_at('age', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(n, mean, sd, median, min, max)%>%
  knitr::kable()
```

### Age bin and sex counts
```{r}
study2_data %>%
  distinct(subid, sex)%>%
  group_by(sex)%>%
  summarise(n = n())%>%
  mutate(total.site.n = sum(n))%>%
  knitr::kable()
```

## Ratings for moral, conventional, conventional-Iran, and religious items
### Descriptives
```{r}
study2_data %>%
  filter(q_kind == 0)%>%
  group_by(task)%>%
  summarise_at('answer', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~median(., na.rm=T),
                    ~min(., na.rm=T),
                    ~max(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(task, n, mean, sd, median, min, max)%>%
  knitr::kable()
```

### Visualization of mean rating (all items collapsed) by site
```{r}
study2_data %>% 
  filter(q_kind == 0)%>%
  mutate(task = factor(task, levels = c("moral", "conv", "conv.iran", "religious"), 
                       labels = c("Moral", "Conventional", "Conventional-Iran", "Religious")))%>%
  ggplot(aes(x = task, y = answer, fill = task, color = task)) + 
  stat_summary(fun = mean, position = position_dodge(width = .9),
               geom="bar", alpha = .5, colour = "black") +
  geom_point(position=position_jitter(width = .18, height = .1),
             size=1.5,
             alpha = .6,
             show.legend=FALSE,
             inherit.aes = TRUE) +
  geom_hline(yintercept = 3.5, color = "grey", linetype = "dashed") + 
  coord_cartesian(ylim = c(1, 6)) +
  stat_summary(fun.data = "mean_cl_boot", geom="linerange", 
               position = position_dodge(width=0.9), size = 1, color = "black") +
  theme(legend.position = "none", 
        # axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(), 
        legend.key.size = unit(.5, 'cm'), 
        legend.text = element_text(size = 10), 
        legend.title = element_text(size = 11), 
        legend.margin=margin(t = 0, unit='cm')) +
  langcog::scale_color_solarized() + 
  langcog::scale_fill_solarized() + 
  labs(y = "Mean rating", 
       x = "Transgression Type") + 
  scale_y_continuous(breaks = seq(1,6, 1))
ggsave("study2_ratings.png", height = 3, width = 6)
```

### Visualization of ratings by age by task
```{r}
study2_data %>%
  filter(q_kind == 0)%>%
  dplyr::rename("Transgression" = "task")%>%
  mutate(Transgression = factor(Transgression, levels = c("moral", "conv", "conv.iran", "religious"), 
                       labels = c("Moral", "Conventional", "Conventional-Iran", "Religious")))%>%
  ggplot(aes(x = age, y= answer, color = Transgression, fill = Transgression)) + 
  geom_point(position = position_jitter(width = .1, height = .05), 
             alpha = .4) + 
  geom_smooth(method ="lm") +
  langcog::scale_color_solarized() + 
  langcog::scale_fill_solarized() + 
  labs(x = "Age", 
       y = "Rating")
```

### Visualization of mean rating (by item) by site
```{r}
study2_data %>% 
  filter(q_kind == 0)%>%
  mutate(task = factor(task, levels = c("moral", "conv", "conv.iran", "religious"), 
                       labels = c("Moral", "Conventional", "Conventional-Iran", "Religious")))%>%
  ggplot(aes(x = item, y = answer, fill =task)) + 
  stat_summary(fun = mean, position = position_dodge(width = .9),
               geom="bar", colour = "black") +
  geom_hline(yintercept = 3.5, color = "grey", linetype = "dashed") + 
  coord_cartesian(ylim = c(1, 6)) +
  facet_grid(~task, scale = "free_x") +
  stat_summary(fun.data = "mean_cl_boot", geom="linerange", 
               position = position_dodge(width=0.9), size = 1, color = "black") +
  theme(legend.position = "none", 
        axis.text.x = element_text(hjust = 1, angle = 45),
        axis.ticks.x = element_blank(), 
        legend.key.size = unit(.5, 'cm'), 
        legend.text = element_text(size = 10), 
        legend.title = element_text(size = 11), 
        legend.margin=margin(t = 0, unit='cm')) +
  langcog::scale_color_solarized() + 
  langcog::scale_fill_solarized() + 
  labs(y = "Mean rating", 
       x = "Situation") + 
  scale_y_continuous(breaks = seq(1,6, 1))
```

### Analyses of differences in rating between moral and conventional transgressions: Within-country
Pre-registered mixed-effects model: Rating ~ Transgression type (moral; conventional; conv.iran, religious)*Age + (Transgression type|Subject) + (age|item).

We will iteratively remove item slopes, then subject slopes, then will remove item effects altogether if necessary.

```{r, include = FALSE}
# set up a df for ratings
ratings.ms <- study2_data %>%
  filter(q_kind == 0)%>%
  mutate(task = factor(task, levels = c("moral", "conv", "conv.iran", "religious")))

#sanity check - every child should have two ratings
ratings.check <-  ratings.ms %>%
  group_by(subid)%>%
  summarise(n = n())%>%
  filter(n <2) #length = 0, so we're okay

set.seed(1234) #set random seed for reproducibility
```

### Model: Answer ~ Task + Age + (1|subid)
**Note** Item model will not converge, so this is our only model

1.  No significant interaction between age and task ($\chi^{2}$ = 5.33, *p* = 0.15)
2.  No significant difference between MORAL and CONVENTIONAL items ($\beta$ = 0.04, *p* = .57)
3.  Significant difference between MORAL and CONVENTIONAL IRAN items ($\beta$ = 0.44, *p* < .001)
4.  No significant difference between MORAL and RELIGIOUS items ($\beta$ = 0.04, *p* = .57)
5.  Significant effect of age ($\beta$ = 0.13, *p* = .01)

```{r, include = FALSE}
iran.rating <- lmer(answer ~ task*age.c + (1|subid), 
                    data = ratings.ms)
##test to see if interaction is significant
iran.rating.base <- lmer(answer ~ task+age.c + (1|subid), 
                    data = ratings.ms)
anova(iran.rating.base, iran.rating, test = 'lrt') #it's not, so don't include it

## get the chisq of the task & age
iran.base.base <-  lmer(answer ~ task + (1|subid), 
                    data = ratings.ms)
anova(iran.base.base, iran.rating.base)
```

```{r}
#summary of item model
knitr::kable(summary(iran.rating.base)$coef)
```

=====
## Judgments of transgression acceptability under certain circumstances 
### Descriptives 
```{r}
study2_data %>%
  filter(q_kind != 0)%>%
  group_by(task, q_kind_label)%>%
  summarise_at('answer', 
               list(~mean(., na.rm=T), 
                    ~sd(., na.rm=T),
                    ~sum(!is.na(.))))%>%
  dplyr::rename("n" = "sum")%>%
  dplyr::select(task, q_kind_label, n, mean, sd)%>%
  knitr::kable()
```

### Visualization of acceptability by task
```{r}
study2_data %>%
  filter(q_kind != 0, 
         q_kind_label != "Haram", 
           q_kind_label != "Illegal",
           q_kind_label != "Zesht")%>%
  mutate(task = factor(task, levels = c("moral", "conv", "conv.iran", "religious"), 
                       labels = c("Moral", "Conventional", "Conventional - Iran", "Religious")), 
         q_kind_label = ifelse(q_kind_label == "Rule at school",
                               "No rule at school", as.character(q_kind_label)), 
         q_kind_label = factor(q_kind_label, levels = c("Faraway country", "No rule at school",
                                                        "Everyone else", "Foreigner", 
                                                        "Non-Muslim")))%>%
  ggplot(aes(x = task, y = answer, fill = task, color = task)) + 
  stat_summary(fun = mean, position = position_dodge(width = .9),
               geom="bar", colour = "black") +
  geom_hline(yintercept = .5, color = "grey", linetype = "dashed") + 
  stat_summary(fun.data = "mean_cl_boot", geom="linerange", 
               position = position_dodge(width=0.9), size = 1, color = "black") +
  facet_grid(~q_kind_label) +
  theme(legend.position = "right", 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), 
        legend.key.size = unit(.5, 'cm'), 
        legend.text = element_text(size = 10), 
        legend.title = element_text(size = 11), 
        legend.margin=margin(t = 0, unit='cm')) +
  langcog::scale_color_solarized() + 
  langcog::scale_fill_solarized() + 
  labs(y = "Mean acceptability rating", 
       x = "", 
       fill = "Transgression") + 
  ggtitle("Would it be okay...") +
  scale_y_continuous(breaks = seq(0, .50, .25))
ggsave("study2_acceptability_ratings_main.png", height = 3, width = 9)

```

### Visualization of illegal, haram, zesht
```{r}
study2_data %>%
  filter(q_kind != 0, 
         q_kind_label == "Haram" | 
           q_kind_label == "Illegal" |
           q_kind_label == "Zesht")%>%
  mutate(task = factor(task, levels = c("moral", "conv", "conv.iran", "religious"), 
                       labels = c("Moral", "Conventional", "Conventional - Iran", "Religious")), 
         q_kind_label = ifelse(q_kind_label == "Haram", "A sin", 
                                      ifelse(q_kind_label == "Zesht", "Rude", "Illegal")))%>%
  ggplot(aes(x = task, y = answer, fill = task, color = task)) + 
  stat_summary(fun = mean, position = position_dodge(width = .9),
               geom="bar", colour = "black") +
  geom_hline(yintercept = .5, color = "grey", linetype = "dashed") + 
  stat_summary(fun.data = "mean_cl_boot", geom="linerange", 
               position = position_dodge(width=0.9), size = 1, color = "black") +
  facet_grid(~q_kind_label) +
  theme(legend.position = "right", 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(), 
        legend.key.size = unit(.5, 'cm'), 
        legend.text = element_text(size = 10), 
        legend.title = element_text(size = 11), 
        legend.margin=margin(t = 0, unit='cm')) +
  langcog::scale_color_solarized() + 
  langcog::scale_fill_solarized() + 
  labs(y = "Mean rating", 
       x = "", 
       fill = "Transgression") + 
  ggtitle("Is it...") +
ggsave("study2_acceptability_ratings_supp.png", height = 3, width = 8.5)

```

### Analysis of acceptability ratings by transgression type: Within-country: 
Pre-registration: Response (yes/no) ~ Transgression type (moral; conventional; conventional-Iran; religious) *Age + (transgression type|subject) +(age|item). Once again we will begin with a maximal random effects structure, and iteratively remove coefficients until the model converges. We will begin first by removing the slope of the item effect, then of subject, and if necessary removing the item effect altogether.


```{r, include = FALSE}
# set up a data frame
acceptability.ms <- study2_data %>%
  filter(q_kind != 0)%>%
  mutate(task = factor(task, levels = c("moral", "conv", "conv.iran", "religious")))
```

#### If everyone else were doing it: Answer ~ Task + Age + (1|subid)
**Note** Model will not converge with item random effect. 

1.  Interaction between task and age not significant, so dropped from the model ($\chi^{2}$ = 6.14, *p* = 0.10)
2.  Significant difference in acceptability between moral and conventional ($\beta$ = 1.26, *p* < .001)
3.  Significant difference in acceptability between moral and conventional-Iran ($\beta$ = 1.84, *p* < .001)
4.  No significant difference in acceptability between moral and religious ($\beta$ = .13, *p* = .70)
5.  Significant effect of age ($\beta$ = 0.92, *p* < .001)

```{r, include = FALSE}
everyone <- glmer(answer ~ task*age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 3),
                    family = 'binomial') # converges

## is the interaction between age and task significant?
everyone.base <- glmer(answer ~ task+age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 3), 
                    family = 'binomial') # converges
anova(everyone.base, everyone, test = 'lrt') ## the interaction does not significantly improve the fit, so we drop it from the model
```

```{r}
##summary of main effects
knitr::kable(summary(everyone.base)$coef)
```

#### Far away: Answer ~ Task + Age + (1|subid)
**Note** Model will not converge with item random effect. 

1.  Interaction between task and age not significant, so dropped from the model ($\chi^{2}$ = 4.00, *p* = 0.26)
2.  Significant difference in acceptability between moral and conventional ($\beta$ = .69, *p* = .03)
3.  Significant difference in acceptability between moral and conventional-Iran ($\beta$ = 1.51, *p* < .001)
4.  Significant difference in acceptability between moral and religious ($\beta$ = 1.70, *p* < .001)
5.  Significant effect of age ($\beta$ = 0.70, *p* = .002)

```{r, include = FALSE}
faraway <- glmer(answer ~ task*age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 1),
                    family = 'binomial') # converges

## is the interaction between age and task significant?
faraway.base <- glmer(answer ~ task+age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 1), 
                    family = 'binomial') # converges
anova(faraway.base, faraway, test = 'lrt') ## the interaction does not significantly improve the fit, so we drop it from the model
```

```{r}
##summary of main effects
knitr::kable(summary(faraway.base)$coef)
```

#### Rule at school: Answer ~ Task + Age + (1|subid)
**Note** Model will not converge with item random effect. 

1.  Interaction between task and age not significant, so dropped from the model ($\chi^{2}$ = 1.08, *p* = 0.78)
2.  Significant difference in acceptability between moral and conventional ($\beta$ = .91, *p* < .001)
3.  Significant difference in acceptability between moral and conventional-Iran ($\beta$ = 1.45, *p* < .001)
4.  Significant difference in acceptability between moral and religious ($\beta$ = 1.00, *p* < .001)
5.  Significant effect of age ($\beta$ = 0.73, *p* = .002)

```{r, include = FALSE}
rule <- glmer(answer ~ task*age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 2),
                    family = 'binomial') # converges

## is the interaction between age and task significant?
rule.base <- glmer(answer ~ task+age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 2), 
                    family = 'binomial') # converges
anova(rule.base, rule, test = 'lrt') ## the interaction does not significantly improve the fit, so we drop it from the model
```

```{r}
##summary of main effects
knitr::kable(summary(rule.base)$coef)
```

#### Foreigner: Answer ~ Task + Age +Task:Age + (1|subid)
**Note** Model will not converge with item random effect. 

1.  Significant interaction between task and age ($\chi^{2}$ = 13.56, *p* = .004)
2.  No significant difference in acceptability between moral and conventional ($\beta$ = .54, *p* =.13)
3.  Significant difference in acceptability between moral and conventional-Iran ($\beta$ = 2.01, *p* < .001)
4.  Significant difference in acceptability between moral and religious ($\beta$ = 1.89, *p* < .001)
5.  Marginal effect of age ($\beta$ = 0.73, *p* = .002)
6.  No significant interaction between age and conventional items ($\beta$ = -0.17, *p* = .60)
7.  No significant interaction between age and conventional-Iran items ($\beta$ = .03, *p* =.92)
8.  Significant interaction between age and religious items (ie, as children age, they are more likely to rate it more acceptable for foreigners to make religious transgressions in comparsion to moral transgressions) ($\beta$ = .78, *p* =.02)

```{r, include = FALSE}
foreigner <- glmer(answer ~ task*age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 4),
                    family = 'binomial', 
                   control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges

## is the interaction between age and task significant?
foreigner.base <- glmer(answer ~ task+age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 4), 
                    family = 'binomial', 
                    control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges
anova(foreigner.base, foreigner, test = 'lrt')
```

```{r}
##summary of main effects
knitr::kable(summary(foreigner)$coef)
```

#### Non-Muslim: Answer ~ Task + Age + Task:Age + (1|subid)
**Note** Model will not converge with item random effect. 

1.  Significant interaction between task and age ($\chi^{2}$ = 15.37, *p* = .002)
2.  No significant difference in acceptability between moral and conventional ($\beta$ = .40, *p* =.30)
3.  Significant difference in acceptability between moral and conventional-Iran ($\beta$ = 1.77, *p* < .001)
4.  Significant difference in acceptability between moral and religious ($\beta$ = 2.38, *p* < .001)
5.  No effect of age ($\beta$ = -0.08, *p* = .83)
6.  Significant interaction between age and conventional items ($\beta$ = 0.85, *p* = .03)
7.  Significant interaction between age and conventional-Iran items ($\beta$ = .77, *p* =.03)
8.  Significant interaction between age and religious items ($\beta$ = 1.38, *p* < .001)

```{r, include = FALSE}
muslim <- glmer(answer ~ task*age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 5),
                    family = 'binomial', 
                   control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges

## is the interaction between age and task significant?
muslim.base <- glmer(answer ~ task+age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 5), 
                    family = 'binomial', 
                    control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges
anova(muslim.base, muslim, test = 'lrt') 
```

```{r}
##summary of main effects
knitr::kable(summary(muslim)$coef)
```

#### Haram: Answer ~ Task + Age + (1|subid)
**Note** Model will not converge with item random effect. 

1.  No significant interaction between task and age ($\chi^{2}$ = 5.59, *p* = .13)
2.  No significant difference between moral and conventional ($\beta$ = -0.41, *p* =.14)
3.  Significant difference between moral and conventional-Iran ($\beta$ = -1.01, *p* < .001)
4.  Significant difference between moral and religious ($\beta$ = 2.02, *p* < .001)
5.  Significant effect of age ($\beta$ = -1.31, *p* < .001)

```{r, include = FALSE}
haram <- glmer(answer ~ task*age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 6),
                    family = 'binomial', 
                   control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges

## is the interaction between age and task significant?
haram.base <- glmer(answer ~ task+age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 6), 
                    family = 'binomial', 
                    control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges
anova(haram.base,haram, test = 'lrt') ## the interaction does not significantly improve the fit, so we drop it from the model
```

```{r}
##summary of main effects
knitr::kable(summary(haram.base)$coef)
```

#### Illegal: Answer ~ Task + Age + (1|subid)
**Note** Model will not converge with item random effect. 

1.  No significant interaction between task and age ($\chi^{2}$ = 1.37, *p* = .71)
2.  No significant difference between moral and conventional ($\beta$ = -0.03, *p* =.90)
3.  Significant difference between moral and conventional-Iran ($\beta$ = -1.50, *p* < .001)
4.  Significant difference moral and religious ($\beta$ = 0.78, *p* = .002)
5.  Significant effect of age ($\beta$ = -1.12, *p* < .001)

```{r, include = FALSE}
illegal <- glmer(answer ~ task*age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 7),
                    family = 'binomial', 
                   control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges

## is the interaction between age and task significant?
illegal.base <- glmer(answer ~ task+age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 7), 
                    family = 'binomial', 
                    control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges
anova(illegal.base,illegal, test = 'lrt') ## the interaction does not significantly improve the fit, so we drop it from the model
```

```{r}
##summary of main effects
knitr::kable(summary(illegal.base)$coef)
```

#### Zesht: Answer ~ Task + Age + (1|subid)
**Note** Model will not converge with item random effect. 

1.  No significant interaction between task and age ($\chi^{2}$ = 1.37, *p* = .71)
2.  Significant difference between moral and conventional ($\beta$ = -1.87, *p* =.02)
3.  Significant difference between moral and conventional-Iran ($\beta$ = -2.85, *p* < .001)
4.  Significant difference between moral and religious ($\beta$ = -2.93, *p* < .001)
5.  Significant effect of age ($\beta$ = -0.54, *p* = .02)
```{r, include = FALSE}
zesht <- glmer(as.factor(answer) ~ task*age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 8),
                    family = 'binomial', 
                   control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges

## is the interaction between age and task significant?
zesht.base <- glmer(as.factor(answer) ~ task+age.c + (1|subid),
                    data = subset(acceptability.ms, q_kind == 8), 
                    family = 'binomial', 
                    control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4))) # converges
anova(zesht.base,zesht, test = 'lrt') ## the interaction does not significantly improve the fit, so we drop it from the model
```

```{r}
##summary of main effects
knitr::kable(summary(zesht.base)$coef)
```

## Now we need to look at how acceptability differs under different circumstances

### ... first is faraway, everyone, rule, foreigner, and muslim 
```{r}
acceptability.limited <- acceptability.ms %>%
  filter(q_kind_label != "Illegal", 
         q_kind_label != "Haram", 
         q_kind_label != "Zesht")


#### visualization
acceptability.limited %>%
  mutate(q_kind_label = ifelse (q_kind_label == "Rule at school", 
                                "No rule at school", as.character(q_kind_label)), 
         q_kind_label = factor(q_kind_label, levels = c("Faraway country", 
                                                        "No rule at school", 
                                                        "Everyone else", 
                                                        "Foreigner",
                                                        "Non-Muslim")))%>%
  mutate(task = factor(task, levels = c("moral", "conv", "conv.iran", "religious"),
                       labels = c("Moral", "Conventional", 
                                  "Conventional - Iran", "Religious")))%>%
  ggplot(aes(x = task, y = answer, fill = q_kind_label)) + 
  stat_summary(fun = mean, position = position_dodge(width = .9),
               geom="bar", colour = "black") +
  stat_summary(fun.data = "mean_cl_boot", geom="linerange", 
               position = position_dodge(width=0.9), size = 1, color = "black") +
  geom_hline(yintercept = .5, color = "grey", linetype = "dashed") + 
  theme(legend.position = "right", 
        legend.key.size = unit(.5, 'cm'), 
        legend.text = element_text(size = 8), 
        legend.title = element_text(size = 9), 
        legend.margin=margin(t = 0, unit='cm'), 
        axis.text.x = element_text(hjust = 1, angle = 45)) +
  scale_fill_brewer(palette = "Dark2") +
  labs(y = "Mean acceptability", 
       x = "", 
       fill = "Situation")
ggsave("circumstances_study2.png", height = 3.5, width = 8)
```

```{r}
## Now run some analyses
######## Moral items first ########
iran.circumstances.base <- glmer(answer ~ age.c + (1|subid), 
                                 family = "binomial", 
                                 data = subset(acceptability.limited, task == "moral"))
## add q kind
iran.circumstances <- glmer(answer ~ q_kind_label + age.c + (1|subid), 
                                 family = "binomial", 
                                 data = subset(acceptability.limited, task == "moral"))
anova(iran.circumstances.base, iran.circumstances, test = 'lrt') #significant effect of circumstances, chisq = 16.724

emmeans::emmeans(iran.circumstances, pairwise~q_kind_label, adjust = "none")
## rule contingency effect for moral items - much more likely to 

######## conventional ########
iran.circumstances.base.conv <- glmer(answer ~ age.c + (1|subid), 
                                 family = "binomial", 
                                 data = subset(acceptability.limited, task == "conv"))
## add q kind
iran.circumstances.conv <- glmer(answer ~ q_kind_label + age.c + (1|subid), 
                                 family = "binomial", 
                                 data = subset(acceptability.limited, task == "conv"))
anova(iran.circumstances.base.conv, iran.circumstances.conv, test = 'lrt') #significant effect of circumstances, chisq = 52.276

emmeans::emmeans(iran.circumstances.conv, pairwise~q_kind_label, adjust = "none")

######## conventional - iran ########
iran.circumstances.base.conv.iran <- glmer(answer ~ age.c + (1|subid), 
                                 family = "binomial", 
                                 data = subset(acceptability.limited, task == "conv.iran"))
## add q kind
iran.circumstances.conv.iran <- glmer(answer ~ q_kind_label + age.c + (1|subid), 
                                 family = "binomial", 
                                 data = subset(acceptability.limited, task == "conv.iran"))
anova(iran.circumstances.base.conv.iran, iran.circumstances.conv.iran, test = 'lrt') #significant effect of circumstances, chisq = 13.401

emmeans::emmeans(iran.circumstances.conv.iran, pairwise~q_kind_label, adjust = "none")

######## religious ########
iran.circumstances.base.religious <- glmer(answer ~ age.c + (1|subid), 
                                 family = "binomial", 
                                 data = subset(acceptability.limited, task == "religious"), 
                                  control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4)))
## add q kind
iran.circumstances.religious <- glmer(answer ~ q_kind_label + age.c + (1|subid), 
                                 family = "binomial", 
                                 data = subset(acceptability.limited, task == "religious"), 
                                  control=glmerControl(optimizer="bobyqa",
                                             optCtrl=list(maxfun=2e4)))
anova(iran.circumstances.base.religious, iran.circumstances.religious, test = 'lrt') #significant effect of circumstances, chisq = 69.814

emmeans::emmeans(iran.circumstances.religious, pairwise~q_kind_label, adjust = "none")
```

## Justifications
```{r}
# Read in the justification data
justifications <- read.csv("../Data/Raw data/Study2/Justifications.csv")%>%
  filter(justifications != "", 
         !is.na(Final.theme))%>%
  mutate(Final.theme = ifelse(Final.theme == " disrespect", "disrespect", 
                              ifelse((Final.theme == "religious " | Final.theme == "reliigious"), "religious", as.character(Final.theme))))
```

### .... visualization of theme x frequency
```{r}
justifications %>%
  group_by(Final.theme)%>%
  summarise(n = n())%>%
  arrange(desc(n))%>%
  mutate(Final.theme = fct_reorder(factor(Final.theme), n, .desc = TRUE))%>%
  ggplot(aes(x = Final.theme, y = n, fill = Final.theme))+
  geom_bar(stat = "identity", color = "black") +
  theme(axis.text.x = element_text(hjust = 1, angle = 45), 
        legend.position = "none") + 
  labs(x = "Justification theme", 
       y = "Frequency") + 
  langcog::scale_fill_solarized("Justification theme")
```

### .... visualization of frequency of justification theme for different kinds of items
```{r}
moral <- c("push", "bad name", "drawing")
conventional <- c("table", "swimsuit", "teacher", "toys", "toys ")
conventional_iran <- c("shoes in house", "back to elder", "drink", "slippers")
religious <- c("fasting", "prayer", "red clothes", "joke")

justifications %>%
  filter(item != "")%>%
  mutate(transgression = ifelse(item %in% moral, "Moral", 
                                ifelse(item %in% conventional, "Conventional", 
                                       ifelse(item %in% conventional_iran, "Conventional-Iran", "Religious"))), 
         transgression = factor(transgression, levels = c("Moral", "Conventional", 
                                                          "Conventional-Iran", "Religious")))%>%
  group_by(transgression, Final.theme)%>%
  summarise(n = n())%>%
  # arrange(desc(n))%>%
  # mutate(Final.theme = fct_reorder(factor(Final.theme), n, .desc = TRUE))%>%
  ggplot(aes(x = Final.theme, y = n, fill = Final.theme))+
  geom_bar(stat = "identity", color = "black") +
  theme(axis.text.x = element_text(hjust = 1, angle = 45), 
        legend.position = "none") + 
  labs(x = "Justification theme", 
       y = "Frequency") + 
  facet_grid(~transgression) +
  langcog::scale_fill_solarized("Justification theme")
ggsave("justifications_theme.png", width = 9, height = 3.5)
```

